Loop Device Performance Overhead for Constraining Batch Job Tasks:\\A Technical Report and Experiment in Metascience

### 2016-05-26 paper.tex
Adds test info printing during experiment run Modifies Makefile to further pipeline each step
Adds first pass content in Reproducibility Concerns section

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Loop Device Performance Overhead for Constraining Batch Job Tasks:\\A Technical Report and Experiment in Metascience}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Nathaniel Kremer-Herman}
\IEEEauthorblockA{Department of Computer Science and Engineering\\University of Notre Dame\\
Email: nkremerh@nd.edu}}

% make the title area
\maketitle

\begin{abstract}
%\boldmath
Providing a resource-constrained sandbox for batch job tasks is a need which has been rising in importance within distributed computing. In many cases, the batch jobs being scheduled are sent to machines which the submitter does not own. Without resource usage guarantees, there is the potential that a task will consume more resources than desired. This may come at the cost of decreasing the availability of the host machine for future work. Or worse, the task may inadvertently take advantage of a flaw which can damage the host machine in an irreparable manner. Presented in this report is a method to keep a batch job task within a secure sandbox constrained by an arbitrary disk size with reasonable performance guarantees as compared to the task executing on the host machine's native filesystem.
\end{abstract}

@@

@@

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

>>>>

\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
\title{Loop Device Performance Overhead for Constraining Batch Job Tasks:\\A Technical Report and Experiment in Metascience}

\author{\IEEEauthorblockN{Nathaniel Kremer-Herman}
\IEEEauthorblockA{Department of Computer Science and Engineering\\University of Notre Dame\\
Email: nkremerh@nd.edu}}

\maketitle

\begin{abstract}
Providing a resource-constrained sandbox for batch job tasks is a need which has been rising in importance within distributed computing. In many cases, the batch jobs being scheduled are sent to machines which the submitter does not own. Without resource usage guarantees, there is the potential that a task will consume more resources than desired. This may come at the cost of decreasing the availability of the host machine for future work. Or worse, the task may inadvertently take advantage of a flaw which can damage the host machine in an irreparable manner. Presented in this report is a method to keep a batch job task within a secure sandbox constrained by an arbitrary disk size with reasonable performance guarantees as compared to the task executing on the host machine's native filesystem.
\end{abstract}

@@

\section{Reproducibility Considerations}
Although this experiment is primarily intended to demonstrate the viability of loop devices for storage constraint, we also make special considerations for the reproducibility of the experiment. In particular, we have already documented a comprehensive specification of the disk used in our test platform. To achieve greater reproducibility however, we must create a near-exact replica of the test platform. This can be done with a virtual machine which will be able to simulate not only the software of the test machine but also the hardware and kernel. The next step toward reproducibility of this work would be for us to host an image of our test platform freely available.

Availability of the experiment is an important consideration for reproducibility. We have provided the source code, which is freely available on GitHub at {\tt{https://github.com/cooperative-computing-lab/disk-alloc-experiment}}. Within this git repository we have included a convenient Makefile which makes running the experiment quite simple. This Makefile downloads all the dependent code for the experiment except some software listed in the {\tt{README}} located in the repository as well as runs the specified tests, generates graphs from the test data, and compiles this paper. We chose to provide this depth of content because reproducibility and availability are high priorities with respect to this technical report.

Another consideration for reproducibility is the anticipated runtime of the tests. In particular, the performance tests (read, write, and file metadata tests) took approximately two weeks to complete on the test platform. This was due to the twenty iterations taken on each test which ran to a nest depth of twenty. This was a heavy I/O load for the test platform. However, the overhead tests (creation and deletion tests) took much less time to run at approximately two hours. The vast difference between the two comes from the lack of nest performance taken into account by the overhead tests.

@@

\ifCLASSOPTIONcaptionsoff
  \newpage
\fi
